A user-extensible and adaptable parser architecture

### 2008-06-02 papers/sgai-2008/paper.tex
Added an example action, rule and log line.

@@

%XXX DO I NEED TO DISCUSS OVERLAPPING RULES\@?

@@

>>>>

Using the \texttt{CONNECT} action as an example, it creates a new data
structure for each client connecting, and saves the data extracted by the
rule (shown in \sectionref{example rule}).  If the data structure already
exists it is treated as a symptom of a bug, and the action issues a warning
containing the full contents of the data structure, plus the log line which
has just been parsed.

@@

@@

\label{example rule}

This example rule matches the message logged by Postfix when a remote
client connects to deliver mail; it would match the following sample log
line:

\begin{verbatim}
    connect from client.example.com[1.2.3.4]
\end{verbatim}

% Don't reformat this!
% XXX CONSIDER USING A TABLE ENVIRONMENT; IT DIDN'T LOOK GREAT BEFORE.
\begin{tabular}[]{ll}
\textbf{Attribute}        & \textbf{Value}                                   \\
program                   & \daemon{smtpd}                                   \\
regex                     & \verb!^connect from (__HOSTNAME__)\[(__IP__)\]$! \\
result\_cols              &                                                  \\
connection\_cols~\empty{} & client\_hostname = 1; client\_ip = 2             \\
action                    & CONNECT                                          \\
priority                  & 0                                                \\
\end{tabular}

\noindent{}The \texttt{CONNECT} action is described in \sectionref{Actions}.
